
\begin{itemize}
\item \textbf{ident} \\
      Molecule name in reference topology.
\item \textbf{maps} \\
      Section containing definitions of mapping schemes.
\item \textbf{maps.map} \\
      Section for a mapping for 1 bead.
\item \textbf{maps.map.name} \\
      Name of the mapping.
\item \textbf{maps.map.weights} \\
      Weights of the mapping matrix. Entries are normalized to 1, number of entries must match the number of reference beads in a coarse-grained bead.
\item \textbf{name} \\
      Name of molecule in coarse-grained representation.
\item \textbf{topology} \\
      Section containing definition of coarse grained topology of molecule.
\item \textbf{topology.cg\_beads} \\
      Section defining coarse grained beads of molecule.
\item \textbf{topology.cg\_beads.cg\_bead} \\
      Definition of a coarse grained bead.
\item \textbf{topology.cg\_beads.cg\_bead.beads} \\
      The beads section lists all atoms of the reference system that are mapped to this particular
      coarse grained bead. The syntax is RESID:RESNAME:ATOMNAME, the beads are seperated by spaces.
\item \textbf{topology.cg\_beads.cg\_bead.mapping} \\
      Mapping scheme to be used for this bead (specified in section mapping) to map from reference system.
\item \textbf{topology.cg\_beads.cg\_bead.name} \\
      Name of coarse grained bead.
\item \textbf{topology.cg\_beads.cg\_bead.type} \\
      Type of coarse grained bead.
\item \textbf{topology.cg\_bonded} \\
      The cg\_bonded section contains all bonded interaction of the molecule. That can be bond, angle or dihedral.
      An entry for each group of bonded interaction can be specified, e.g. several groups (types) of bonds can be specified.
      A specific bonded interaction can be later on addressed by MOLECULE:NAME:NUMBER, where MOLECULE is the molecule ID in
      the whole topology, NAME the name of the interaction group and NUMBER addresses the interaction in the group.
\item \textbf{topology.cg\_bonded.angle} \\
      Definition of a group of angles.
\item \textbf{topology.cg\_bonded.angle.beads} \\
      List of triples of beads that define a bond. Names specified in cg\_beads, separated by commas.
\item \textbf{topology.cg\_bonded.angle.name} \\
      Name of the group.
\item \textbf{topology.cg\_bonded.bond} \\
      Definition of a group of bonds.
\item \textbf{topology.cg\_bonded.bond.beads} \\
      List of pair of beads that define a bond. Names specified in cg\_beads, separated by commas.
\item \textbf{topology.cg\_bonded.bond.name} \\
      Name of the group.
\item \textbf{topology.cg\_bonded.dihedral} \\
      Definition of a group of dihedrals. Since the exact functional form does not matter, this combines proper as well as improper dihedrals.
\item \textbf{topology.cg\_bonded.dihedral.beads} \\
      List of quadruples of beads that define a bond. Names specified in cg\_beads, separated by commas.
\item \textbf{topology.cg\_bonded.dihedral.name} \\
      Name of the group.
\end{itemize}
