\section{Iterative Inversion Scripts}

\subsection{Basic workflow}
This set of scripts implement iterative boltzmann inversion + inverse monte carlo. 

To setup the environment, run:
csh, tcsh: source `<csg-installation>/bin/CSGRC.csh
bash: source `<csg-installation>/bin/CSGRC.bash   

tutorials can be found in
<csg-installation>/share/csg/tutor

just copy tip3p and try 
  ./run.sh cg.xml

Each iteration is divided n several steps:

run the simulation

calculate statistics + delta U

a file <name>.dpot.new is created

post\_update: (called for each interaction)

 here the user can hook in several scripts to act on dU. One example for that is pressure correction. Also 
smoothing/extrapolation is possible

 each script reads a <name>.dpot.cur and writees <name>.dpot.new. The inverse script takes care for correct renaming and saving all the intermediate steps in <name>.dpot.X where X is a number.
Add the potentials (called for each interaction)
\begin{equation}
  U_{n+1} = U_n + \Delta U
\end{equation}

write CG-CG.pot.new

Post add (called for each interaction)

do manipulations on the potential like smoothing,...

similiar behaviour as post\_update, just acting on <name>.pot.cur, <name>.pot.new

\subsection{input}
For options + directives see ...

As target distribution, any table file can be given (e.g. gromacs output from g\_rdf). The program automaticaly takes care to resample to the correct grid spacing in the .xml file.

The initial guess is created by inverting the rdf. It's located in step\_00/<name>.pot.new. To create an own initial guess, place a file called <name>.pot.in in your folder where you run the scripts.

Also all the files to run a simulation have to be created:
conf.gro
table.xvg  (if using energy\_grp\_tables give any standard file here)
topol.top
grompp.mdp

These files have to be specified in the xml file (see tutorial or [[Coarse graining directives]])


\subsection{post processing}
== smooth ==
does a simple triangular smooth on the active range.
you can specify the number of smoothing iterations in <post\_update\_options><smooth><iterations>

\subsection{Customization}
Please never ever change our installed scripts. You can hook in your own scripts for any single sub part. The file
<csg-install>/share/csg/scripts/inverse/csg\_table assigns to two given keywords a script which is called. You can change this by creating a file
csg\_table in your own directory (specified in the Coarse graining directives). Just add a line for each script you want to add or change. The source\_wrapper takes care that your script is called instead of the one from the standard installations. For scripting details have a look at the source, there is no developers manual so far. Feel free to ask Christoph Junghans or Victor Rühle for details.
